{
\def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi}
\begin{tabular}{l*{4}{c}}
\hline\hline
                &\multicolumn{4}{c}{Preference for Majority Method}                         \\\cmidrule(lr){2-5}
                &\multicolumn{1}{c}{(1)}         &\multicolumn{1}{c}{(2)}         &\multicolumn{1}{c}{(3)}         &\multicolumn{1}{c}{(4)}         \\
\hline
Negative CCP Narrative&   -0.070         &   -0.063         &   -0.089         &   -0.080         \\
                &  (0.073)         &  (0.087)         &  (0.072)         &  (0.088)         \\
[1em]
Positive CCP Narrative&   -0.023         &   -0.016         &   -0.043         &   -0.033         \\
                &  (0.072)         &  (0.087)         &  (0.071)         &  (0.087)         \\
[1em]
Neutral Narrative&                  &    0.014         &                  &    0.019         \\
                &                  &  (0.100)         &                  &  (0.099)         \\
\hline
Observations    & 1107.000         & 1107.000         & 1107.000         & 1107.000         \\
R-squared       &    0.001         &    0.001         &    0.051         &    0.051         \\
Gender          &                  &                  &$\checkmark$         &$\checkmark$         \\
Parents' Urban Controls&                  &                  &$\checkmark$         &$\checkmark$         \\
Country of Birth FE&                  &                  &$\checkmark$         &$\documentclass[]{article}
\usepackage{amssymb}
\usepackage{adjustbox}
\usepackage{booktabs}
\usepackage{changepage}
\begin{document}
{
\def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi}
\begin{tabular}{l*{4}{c}}
\hline\hline
                &\multicolumn{4}{c}{Preference for Majority Method}                         \\\cmidrule(lr){2-5}
                &\multicolumn{1}{c}{(1)}         &\multicolumn{1}{c}{(2)}         &\multicolumn{1}{c}{(3)}         &\multicolumn{1}{c}{(4)}         \\
\hline
Negative CCP Narrative     &   -0.070         &   -0.063         &   -0.089         &   -0.080         \\
                &  (0.073)         &  (0.087)         &  (0.072)         &  (0.088)         \\
[1em]
Positive CCP Narrative     &   -0.023         &   -0.016         &   -0.043         &   -0.033         \\
                &  (0.072)         &  (0.087)         &  (0.071)         &  (0.087)         \\
[1em]
Neutral Narrative       &                  &    0.014         &                  &    0.019         \\
                &                  &  (0.100)         &                  &  (0.099)         \\
\hline
Observations    & 1107        & 1107        & 1107        & 1107         \\
R-squared       &    0.001         &    0.001         &    0.051         &    0.051         \\
\hline
Gender          &                  &                  &$\checkmark$         &$\checkmark$         \\
Parents' Urban Controls&                  &                  &$\checkmark$         &$\checkmark$         \\
Country of Birth FE&                  &                  &$\checkmark$         &$\checkmark$         \\
Mother's Country FE&                  &                  &$\checkmark$         &$\checkmark$         \\
Father's Country FE&                  &                  &$\checkmark$         &$\checkmark$         \\
Parents' Educational Attainment&                  &                  &$\checkmark$         &$\checkmark$         \\
        \hline\hline        
\end{tabular}   \\        
\begin{adjustwidth}{-1cm}{-1cm}             
    \begin{scriptsize}       
    The table shows that exposing participants to different narratives about the policies of the Chinese Communist Party has an insignificant and economically small effect on behavior in the task. Each column reports the coefficients from a single OLS regression of the dependent variable described in the column heading on the variable described in the row heading. An observation is an émigré from Greater China living in North America who was recruited via Facebook targeted ads to complete an online survey (see Section I.B and online Appendix B.1 for further details about the data collection). Majority Method is the preference over a method to assign a decision for a group in the incentivized task, with one corresponding to a strong preference for a decision by an authority designated by the experimenter, and 5 corresponding to a strong preference for majority rule.  Positive CCP Narrative, Negative CCP Narrative, and Neutral Narrative are indicators that equal 1 if, before participating in the decision task, the respondent was shown a message containing a narrative that casts a positive, negative, or neutral light on the CCP (see Appendix A.1 for more information about these indicators). Gender is an indicator that equals one if the respondent reports identifying as a female, 0 otherwise. Country of Birth FE, Mother Country FE, and Father Country FE correspond to fixed effects for the respondent's, her mother's, and her fathers countries of birth, respectively. Parents' Educational Attainment corresponds to indicators for whether each parent completed high school or more. Parents' Urban Controls corresponds to indicators for whether each parent came from an urban background. Robust standard errors are in parenthesis.             
    \end{scriptsize} 
\end{adjustwidth}

\end{document}\checkmark$         \\
Mother's Country FE&                  &                  &$\checkmark$         &$\checkmark$         \\
Father's Country FE&                  &                  &$\checkmark$         &$\checkmark$         \\
Parents' Educational Attainment&                  &                  &$\checkmark$         &$\checkmark$         \\
        \hline\hline        \end{tabular}            \begin{adjustwidth}{-1cm}{-1cm}              \begin{scriptsize}        Each column reports the coefficients from a single OLS regression of the dependent variable described in the column heading on the variable described in the row heading. An observation is an émigré from Greater China living in North America who was recruited via Facebook targeted ads to complete an online survey (see Section I.B and online Appendix B.1 for further details about the data collection). Majority Method is the preference over a method to assign a decision for a group in the incentivized task, with one corresponding to a strong preference for a decision by an authority designated by the experimenter, and 5 corresponding to a strong preference for majority rule.  Positive CCP Narrative, Negative CCP Narrative, and Neutral Narrative are indicators that equal 1 if, before participating in the decision task, the respondent was shown a message containing a narrative that casts a positive, negative, or neutral light on the CCP (see Appendix A.1 for more information about these indicators). Gender is an indicator that equals one if the respondent reports identifying as a female, 0 otherwise. Country of Birth FE, Mother Country FE, and Father Country FE correspond to fixed effects for the respondent's, her mother's, and her fathers countries of birth, respectively. Parents' Educational Attainment corresponds to indicators for whether each parent completed high school or more. Parents' Urban Controls corresponds to indicators for whether each parent came from an urban background. Robust standard errors are in parenthesis.        \end{scriptsize} \end{adjustwidth}
